Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-18 forecast/paper/paper.tex
abstract (241 words)

\begin{abstract}
Please provide an abstract of no more than 250 words in a single paragraph.
Abstracts should explain to the general reader the major contributions of the
article. References in the abstract must be cited in full within the abstract
itself and cited in the text. 
\end{abstract}

>>>>

\begin{abstract}
Reliable short-term, location-specific forecasts of a pandemic are a
key ingredient in effective public health decision making. Through the
COVID-19 pandemic, a plethora of real-time data signals were
collected, curated, and made publicly available by our team and data
partners, providing multiple views of the pandemic's progress. The
goal of this work is to measure the practical utility of these
auxiliary indicators from a forecasting perspective. We focus on five
indicators, derived from medical insurance claims data, web search
queries, and survey responses. For each indicator, we ask whether
including it in a simple model leads to improved forecasting
performance relative to a similar model without it. Performance is considered across two tasks
at the state level at a forecasting horizon of up to about one month:
Probabilistic forecasting of seven-day average case rates and binary
prediction of ``hotspots.'' Since the values of indicators are
commonly revised over time, we take special care to ensure that the data provided
to a forecaster is the version that would have been available at the
time that the forecast was made. We demonstrate how less careful
backtesting can lead to misleading retrospective evaluations. Our analysis suggests consistent, although
modest, gains in forecasting performance by using these indicators,
and we investigate whether the auxiliary signals are acting as ``leading indicators'' of case rates.
Evaluating forecasters thoroughly and fairly is an important way that
we can learn from this pandemic to do better in the next.

% Please provide an abstract of no more than 250 words in a single paragraph.
% Abstracts should explain to the general reader the major contributions of the
% article. References in the abstract must be cited in full within the abstract
% itself and cited in the text.
\end{abstract}
